Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-11 podc16/paper2.tex
typos

The graph processing algorithm must compute $\opn{c-struct}\left( g_p \right)$, as defined below.
Its main property is Lemma 1; Together with Invariants 1 and 2 (TODO, the invariants guaranteed by the dependency-set algorithm and the map-agreement algorithm), Lemma 1 implies that leaderless algorithms safely implement generalized consensus.

@@

\textbf{Graph of strongly connected components.} Given a graph $g$, let $\hat{g}$ be the graph whose vertices are the strongly connected components of $g$ (represented as sets of vertices) and where there is an edge from $g_1$ to $g_2$ if and only if there are two vertices $v_1$ and $v_2$ of $g$ such that $v_1 \in V\left( g_1 \right)$, $v_2 \in V\left( g_2 \right)$, and $\left( v_1,v_2 \right)\in E\left( g \right)$. Note that the reflexive and transitive closure of $V\left(  \hat{g} \right)$ is necessarily a partial order. 
For example, consider $h$ such that $V\left( h \right)=\aset{c_1,c_2,c_3,c_4}$ and $E\left( h \right)=\aset{\left( c_1,c_2 \right),\left( c_2,c_1 \right),\left( c_1,c_3 \right)}$. Then $V\left(\hat{h}\right) = \aset{\aset{c_1,c_2},\aset{c_3},\aset{c_4}}$ and $E\left( \hat{h} \right)=\aset{\left( \aset{c_1,c_2},\aset{c_3} \right)}$. We will use $h$ as an example in the rest of the section.

@@

\textbf{Linearizations of a dependency graph.}
When $\hat{o}$ is a total order over the strongly connected components of $g$ such that $\hat{o} \in \opn{TOs}\left( \hat{g} \right)$, we say that a total order $l$ on $V\left( g \right)$ is a \emph{linearization} of $g$ when $\left(v_1,v_2\right) \in l$ iff (1) there exists $vs_1,vs_2\in V\left(\hat{g}\right)$ such that $v_1\in vs_1$, $v_2\in vs_2$, and $\left( vs_1,vs_2 \right)\in \hat{o}$, or (2) there exists $vs_1\in V\left(\hat{g}\right)$ such that
$v_1,v_2\in  vs_1$ and $\left( v_1,v_2 \right)\in f\left[  vs_1 \right]$.
For example, if $f\left[ \set{c_1,c_2} \right] = \aseq{c_2,c_1}$ then $\aseq{c_2,c_1,c_3,c_4}$ is a linearization of $h$ but $\aseq{c_1,c_2,c_3,c_4}$ is not and neither is $\aseq{c_3,c_2,c_1,c_4}$

\textbf{Partial order on graphs.}
If $g_1$ and $g_2$ are two graphs, then we write $g_1 \leq g_2$ iff $V\left( g_1 \right)\subseteq V\left( g_2 \right)$, and if $v\in V\left( g_1 \right)$, $e\in E\left( g_2 \right)$, and $v$ is an endpoint of $e$, then $e\in E\left( g_1 \right)$. 
For example, if $V\left( h' \right)=\aset{c_1,c_2,c_4}$ and $E\left( h' \right)=\aset{\left( c_1,c_2 \right),\left( c_2,c_1 \right)}$ then $h'\leq h$. However, if $V\left( h'' \right)=\aset{c_1,c_3,c_4}$ and $E\left( h \right)=\aset{\left( c_1,c_3 \right)}$ then $\left( h'',h \right)\notin \leq$.

>>>>

The graph processing algorithm is executed locally by a node. It must compute $\opn{c-struct}\left( g_p \right)$, as defined below.
Its main property is Lemma 1; Together with Invariants 1 and 2 (TODO, the invariants guaranteed by the dependency-set algorithm and the map-agreement algorithm), Lemma 1 implies that leaderless algorithms safely implement generalized consensus. 
To execute the graph processing

@@

\textbf{Graph of strongly connected components.} Given a graph $g$, let $\hat{g}$ be the graph whose vertices are the strongly connected components of $g$ (represented as sets of vertices) and where there is an edge from $g_1$ to $g_2$ if and only if there are two vertices $v_1$ and $v_2$ of $g$ such that $v_1 \in V\left( g_1 \right)$, $v_2 \in V\left( g_2 \right)$, and $\left( v_1,v_2 \right)\in E\left( g \right)$. Note that the reflexive and transitive closure of $V\left(  \hat{g} \right)$ is necessarily a partial order. 
For example, consider $h$ such that $V\left( h \right)=\aset{c_1,c_2,c_3,c_4}$ and $E\left( h \right)=\aset{\left( c_1,c_2 \right),\left( c_2,c_1 \right),\left( c_1,c_3 \right)}$. Then $V(\hat{h}) = \aset{\aset{c_1,c_2},\aset{c_3},\aset{c_4}}$ and $E( \hat{h} )=\aset{\left( \aset{c_1,c_2},\aset{c_3} \right)}$. We will use $h$ as an example in the rest of the section.

@@

\textbf{Linearizations of a dependency graph.}
When $\hat{o}$ is a total order over the strongly connected components of $g$ such that $\hat{o} \in \opn{TOs}\left( \hat{g} \right)$, we say that a total order $l$ on $V\left( g \right)$ is a \emph{linearization} of $g$ when $\left(v_1,v_2\right) \in l$ iff (1) there exists $vs_1,vs_2\in V\left(\hat{g}\right)$ such that $v_1\in vs_1$, $v_2\in vs_2$, and $\left( vs_1,vs_2 \right)\in \hat{o}$, or (2) there exists $vs_1\in V\left(\hat{g}\right)$ such that
$v_1,v_2\in  vs_1$ and $\left( v_1,v_2 \right)\in f\left[  vs_1 \right]$.
For example, if $f\left[ \aset{c_1,c_2} \right] = \aseq{c_2,c_1}$ then $\aseq{c_2,c_1,c_3,c_4}$ is a linearization of $h$ but $\aseq{c_1,c_2,c_3,c_4}$ is not and neither is $\aseq{c_3,c_2,c_1,c_4}$

\textbf{Partial order on graphs.}
If $g_1$ and $g_2$ are two graphs, then we write $g_1 \leq g_2$ iff $V\left( g_1 \right)\subseteq V\left( g_2 \right)$, and if $v\in V\left( g_1 \right)$, $e\in E\left( g_2 \right)$, and $v$ is an endpoint of $e$, then $e\in E\left( g_1 \right)$. 
For example, if $V\left( h' \right)=\aset{c_1,c_2,c_4}$ and $E\left( h' \right)=\aset{\left( c_1,c_2 \right),\left( c_2,c_1 \right)}$ then $h'\leq h$. However, if $V\left( h'' \right)=\aset{c_1,c_3,c_4}$ and $E\left( h'' \right)=\aset{\left( c_1,c_3 \right)}$ then $\left( h'',h \right)\notin \leq$.
